Summarize distribution of LR statistic under null

### 2017-01-15 analysis/investigate_hu_badcoverage.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ashr)
library(reshape2)
library(ggplot2)
library(dplyr)
library(dscr)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(ashr)
library(reshape2)
library(ggplot2)
library(dplyr)
library(dscr)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/make_GOODPOOR_figs.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

First, we load the necessary libraries and function definitions, and specify 
settings for displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ashr)
library(qvalue)
library(locfdr)
library(mixfdr)
library(ggplot2)
source("chunk-options.R")
source("../R/plot_FDReg_hist.R")
```

>>>>

First, we load the necessary libraries and function definitions.

```{r packages}
library(ashr)
library(qvalue)
library(locfdr)
library(mixfdr)
library(ggplot2)
source("../R/plot_FDReg_hist.R")
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/makefig_FDReg.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ashr)
library(qvalue)
library(locfdr)
library(mixfdr)
source("chunk-options.R")
source("../R/plot_FDReg_hist.R")
source("../R/nullalthist.R")
```

>>>>

First, we load the necessary libraries and function definitions.

```{r packages}
library(ashr)
library(qvalue)
library(locfdr)
library(mixfdr)
source("../R/plot_FDReg_hist.R")
source("../R/nullalthist.R")
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/metaplot_examples.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(knitr)
library(rmeta)
library(ashr)
source("chunk-options.R")
opts_chunk$set(echo = TRUE)
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(knitr)
library(rmeta)
library(ashr)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
opts_chunk$set(echo = TRUE)
```

### 2017-01-15 analysis/plot_cdf_eg.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(plyr)
library(dplyr)
library(magrittr)
library(ashr)
library(ggplot2)
library(dscr)
library(REBayes)
library(ashr)
source("chunk-options.R")
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

>>>>

First, we load the necessary libraries and useful function definitions.

```{r packages}
library(plyr)
library(dplyr)
library(magrittr)
library(ashr)
library(ggplot2)
library(dscr)
library(REBayes)
library(ashr)
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/plot_egdens.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

```{r chunk_options, include=FALSE}
library(ashr)
library(ggplot2)
library(dplyr)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(ashr)
library(ggplot2)
library(dplyr)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/plot_lfsr.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(dplyr)
library(reshape2)
library(ggplot2)
source("chunk-options.R")
source("../R/set_plot_colors.R")
```

>>>>

First, we load the necessary libraries and other useful function definitions.

```{r packages}
library(dplyr)
library(reshape2)
library(ggplot2)
source("../R/set_plot_colors.R")
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/plot_pi0est.Rmd
Successfully re-knit plot_pi0est.Rmd.
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

```{r chunk_options, include=FALSE}
library(magrittr)
library(dplyr)
source("chunk-options.R")
source("../R/set_plot_colors.R")
```

*Explain here what this chunk does.*

>>>>

```{r packages}
library(magrittr)
library(dplyr)
source("../R/set_plot_colors.R")
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

Generate scatterplots compare the estimated estimate of pi0 against the 
ground-truth value, colored by the method used, and split by the scenario
type.

### 2017-01-15 analysis/summarize_coverage.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(dscr)
library(ashr)
library(reshape2)
library(ggplot2)
library(magrittr)
library(dplyr)
library(xtable)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(dscr)
library(ashr)
library(reshape2)
library(ggplot2)
library(magrittr)
library(dplyr)
library(xtable)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```

### 2017-01-15 analysis/summarize_dsc_znull.Rmd
Split setting chunk options and loading packages into separate chunks; re-rendered investigate_hu_badcoverage.Rmd, make_GOODPOOR_figs.Rmd, makefig_FDReg.Rmd, metaplot_examples.Rmd, plot_cdf_eg.Rmd, plot_egdens.Rmd, plot_lfsr.Rmd and plot_pi0est.Rmd.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ggplot2)
library(dplyr)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(ggplot2)
library(dplyr)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```
